The Unified Nature of the Dielectric Properties of Two-Dimensional Materials

### 2018-11-12 paper.tex
Merge new fig1 and fig2 with the main text

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Jonathan Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
\author{Manish Chhowalla}
\affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\date{}
\title{Unified Understanding of the Dielectric Nature of Two-Dimensional Materials}
\begin{document}

@@

\section{Introduction}
\label{sec:org2ea169d}

The central place of dielectric properties, especially the static
dielectric constant in material research
\cite{Dressel_2001_electrodynamics} drives the pursuit for a unified
model between the electronic and dielectric properties of materials.
In fact, some pioneering work\cite{Moss_1950_relation} discovered
relations between the dielectric constant $\varepsilon$ and other
physical properties, in particular the band gap $E_{\mathrm{g}}$
(minimal optical transition energy) of bulk
semiconductors. Moss\cite{Moss_1950_relation,Moss_1985_n_Eg} showed
that $E_{\mathrm{g}}$ and $\varepsilon$ follow a semi-empirical
relation, known as the Moss relation:
\begin{equation}
\label{eq:Moss-relations}
\varepsilon^{2} E_{\mathrm{g}} \approx 95\ \mathrm{eV}
\end{equation}
Other similar semi-empirical models for the relations between
$\varepsilon$ and $E_{\mathrm{g}}$ of bulk semiconductors have also
been proposed
\cite{Ravindra_1979_eps_Eg,Ravindra_1980_model,Ravindra_2007_Eg_rev}. Despite
the minor difference between the formulae used, it is clear that there
exists certain general electronic relations in bulk
semiconductors. The existence of such general relationship is also of
high practical importance: it is generally more straightforward and
accurate to measure the band gap $E_{\mathrm{g}}$ than the static
dielectric constant $\varepsilon$, as the latter is strongly dependent
on several critical details on the sample measurements, such as
contamination, disorder, and model interpretation. With the Moss
relationship or other similar models, it is feasible to predict the
dielectric constant of a bulk semiconductor with a reasonable degree
of certainty.

>>>>

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Jonathan Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
\author{Manish Chhowalla}
% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
\affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kindom}
\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\date{}
\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
% \title{Unified Understanding of the Dielectric Nature of Two-Dimensional Materials}
\begin{document}

@@

% \section{Introduction}
% \label{sec:org2ea169d}
\linenumbers{}

{\bfseries Dielectric constant, which defines the polarization of the
  media, is a key quantity in condensed matter. Here we show that
  despite its fundamental transcendence, the dielectric constant does
  not define unequivocally the dielectric properties of a
  two-dimensional (2D) material. We found instead that the dielectric
  polarizability correctly captures the dielectric nature of a 2D
  material which is strongly dependent on the long-range
  electron-electron interaction.  We reveal a long-sought universal
  framework where electronic, geometrical and dielectric properties
  are intrinsically correlated through the polarizability opening the
  door to probe quantities yet not directly measurable, e.g. thickness
  of an atom.  By using this framework, we unify the concept of
  dielectric properties in any material dimension through a dielectric
  anisotropy index which defines the degree of controllability of the
  dielectric features of a compound. A universal boundary line
  separates the 3D and 2D behaviors where materials likely to have
  similar properties as layered materials collapsed onto.  }

The central place of dielectric properties, especially the static
dielectric constant in material research
\cite{Dressel_2001_electrodynamics} drives the pursuit for a unified
model between the electronic and dielectric properties of materials.
In fact, some pioneering work\cite{Moss_1950_relation} discovered
relations between the dielectric constant $\varepsilon$ and other
physical properties, in particular the band gap $E_{\mathrm{g}}$ of bulk
semiconductors. Moss\cite{Moss_1950_relation,Moss_1985_n_Eg} showed
that $E_{\mathrm{g}}$ and $\varepsilon$ follow a semi-empirical
relation, known as the Moss relation:
\begin{equation}
\label{eq:Moss-relations}
\varepsilon^{2} E_{\mathrm{g}} \approx 95\ \mathrm{eV}
\end{equation}
Other similar semi-empirical models for the relations between
$\varepsilon$ and $E_{\mathrm{g}}$ of bulk semiconductors have also
been proposed
\cite{Ravindra_1979_eps_Eg,Ravindra_1980_model,Ravindra_2007_Eg_rev}. Despite
the minor difference between the formulae used, it is clear that there
exists certain general electronic relations in bulk
semiconductors. The existence of such general relationship is also of
high practical importance: it is generally more straightforward and
accurate to measure the band gap $E_{\mathrm{g}}$ than the static
dielectric constant $\varepsilon$, as the latter is strongly dependent
on several critical details on the sample measurements, such as
contamination, disorder, and model interpretation. With the Moss
relationship or other similar models, it is feasible to predict the
dielectric constant of a bulk semiconductor with a reasonable degree
of certainty.
